A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-01-28 article.tex
加入子系统变工况用损率分析图
1修改新系统图 2完成latex转换

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
\caption{Boiler internal heat exchangers layout} 
\label{fig:boiler_surface}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/novel_system}
\caption{Schematic of the novel system} 
\label{fig:novel_system}
\end{figure}

@@

\subsection{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. 
The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
% The novel system’s parameters are based on reference system, so the main parameters must be the same. The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc. The main parameters settled under THA situation can be found in Table 1 and Table 4 . 
% 对于新旧系统表格的热力参数进行分析，下面这段话太少

\begin{table}
\caption{Thermodynamic performance of the reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in generating efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}
% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
The results of exergy analysis of the optimization system are presented in Table~\ref{table:system exergy campare}. 
It is found that the optimization system has an improvement in exergetic performance.
 The total exergy destruction of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
 The new system also brings the improvement from 46.98\% to 47.99\%. 
 Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. 
 For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

@@

\begin{table}
\caption{Systems' exergy destruction rate comparison }
\label{table:system exergy campare}
\centering
\begin{tabular}{lll}
\toprule 
Items & Reference System\,(MW) & Novel System\,(MW)\tabularnewline
\midrule 
Boiler(without AP) & 883.26 & 872.22\tabularnewline
Turbine & 63.33 & 63.97\tabularnewline
Air Preheater  & 27.39 & 16.55\tabularnewline
Regenerative system & 22.53 & 21.56\tabularnewline
Other & 131.03 & 142.42 \tabularnewline
Total & 1116.72 & 1127.54\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\label{table:extraction compare}
\caption{Systems' extractions comparison}
\begin{centering}
\begin{tabular}{llll}
\toprule 
\multirow{2}{*}{Extractions} & \multirow{2}{2.5cm}{Reference system (kg/s)} & \multicolumn{2}{c}{Novel system (kg/s)}\tabularnewline
\cmidrule{3-4} 
 &  & to RHs & to APHs\tabularnewline
\midrule
1st & 54.47 & 43.79 & 15.42\tabularnewline
2nd & 52.18 & 18.52 & 13.5\tabularnewline
3rd & 37.86 & 31.71 & 14.62\tabularnewline
4th & 20.53 & 5.66 & 9.5\tabularnewline
5th & 11.95 & 9.78 & 5.67\tabularnewline
6th & 19.94 & 9.88 & 7.83\tabularnewline
7th & 30.19 & 14.16 & 12.85\tabularnewline
8th & 16.31 & 3.11 & 27.1\tabularnewline
9th & 18.93 & 18.93 & 0\tabularnewline
10th & 20.61 & 20.6 & 0\tabularnewline
Total & 282.97 & 176.14 & 106.49\tabularnewline
\bottomrule
\end{tabular}
\par\end{centering}
\end{table}
% 下面两段话需要根据图修改
The variation of mass flow rate of extractions is presented in Fig 6.
 Mass flow rate of the 1st, 3rd, 5th and 8th extractions of the optimization system is more than that of the base model, and the rest extractions except the last two, has the opposite variation. 
 The impact of system optimization on extraction is twofold. 
 Air is heated by extractions, which will cause an increment in mass flow. 
 And the use of LPE can saves extractions.so the total extraction keeps unchanged.
 Turbine total extraction steam volume change affect its exergy efficiency by 2.03\%.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.png}
\caption{T-Q diagram of Air preheat subsystems} 
\label{fig:APH_temper_compare}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} 
\label{fig:novel_APH_exergy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
\caption{Exergy efficiency in off-design conditions} 
\label{fig:partload_efficiency}
\end{figure}

% subsubsection subsubsection_name (end)
\section*{References}
\bibliographystyle{elsarticle-num}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
\caption{Boiler internal heat exchangers layout} 
\label{fig:boiler_surface}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/novel_system.png}
\caption{Schematic of the novel system} 
\label{fig:novel_system}
\end{figure}

@@

\subsection{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}

\subsubsection{Thermodynamic comparison in design condition}
\label{ssub:desing_compare}
Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. 
The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
% The novel system’s parameters are based on reference system, so the main parameters must be the same. The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc. The main parameters settled under THA situation can be found in Table 1 and Table 4 . 
% 对于新旧系统表格的热力参数进行分析，下面这段话太少

\begin{table}
\caption{Thermodynamic performance of reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in generating efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}
% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
The results of exergy analysis of the optimization system are presented in Table~\ref{table:system exergy campare}. 
It is found that the optimization system has an improvement in exergetic performance.
 The total exergy destruction of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
 The new system also brings the improvement from 46.98\% to 47.99\%. 
 Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. 
 For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

@@

\begin{table}
\caption{Exergy destruction rate comparison of reference and novel systems }
\label{table:system exergy campare}
\centering
\begin{tabular}{lll}
\toprule 
Items & Reference System\,(MW) & Novel System\,(MW)\tabularnewline
\midrule 
Boiler(without AP) & 883.26 & 872.22\tabularnewline
Turbine & 63.33 & 63.97\tabularnewline
Air Preheater  & 27.39 & 16.55\tabularnewline
Regenerative system & 22.53 & 21.56\tabularnewline
Other & 131.03 & 142.42 \tabularnewline
Total & 1116.72 & 1127.54\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\label{table:extraction compare}
\caption{Extractions comparison of reference and novel systems}
\begin{centering}
\begin{tabular}{llll}
\toprule 
\multirow{2}{*}{Extractions} & \multirow{2}{2.5cm}{Reference system (kg/s)} & \multicolumn{2}{c}{Novel system (kg/s)}\tabularnewline
\cmidrule{3-4} 
 &  & to RHs & to APHs\tabularnewline
\midrule
1st & 54.47 & 43.79 & 15.42\tabularnewline
2nd & 52.18 & 18.52 & 13.5\tabularnewline
3rd & 37.86 & 31.71 & 14.62\tabularnewline
4th & 20.53 & 5.66 & 9.5\tabularnewline
5th & 11.95 & 9.78 & 5.67\tabularnewline
6th & 19.94 & 9.88 & 7.83\tabularnewline
7th & 30.19 & 14.16 & 12.85\tabularnewline
8th & 16.31 & 3.11 & 27.1\tabularnewline
9th & 18.93 & 18.93 & 0\tabularnewline
10th & 20.61 & 20.6 & 0\tabularnewline
Total & 282.97 & 176.14 & 106.49\tabularnewline
\bottomrule
\end{tabular}
\par\end{centering}
\end{table}
% 下面两段话需要根据图修改
%对于新系统优化可二次再热后蒸汽的抽汽，使8th抽汽量增加
The variation of mass flow rate of extractions is presented in Fig 6.
 Mass flow rate of the 1st, 3rd, 5th and 8th extractions of the optimization system is more than that of the base model, and the rest extractions except the last two, has the opposite variation. 
 The impact of system optimization on extraction is twofold. 
 Air is heated by extractions, which will cause an increment in mass flow. 
 And the use of LPE can saves extractions.so the total extraction keeps unchanged.
 Turbine total extraction steam volume change affect its exergy efficiency by 2.03\%.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/APH_temper_compare.png}
\caption{T-Q diagram of Air preheat subsystems} 
\label{fig:APH_temper_compare}
\end{figure}
% 在空气预热开始时，在第8级空预器出换热量和换热温差均较大，使之成为用损最大的换热器，随着空气预热的继续进行，换热温差降低，低1-7级空预器的用损减小。当空气进入AOC时，由于抽汽温度较高，所以换热温差增大，但由于换热量较小，造成在AOC中的用损失较小。
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{fig/novel_APH_exergy.png}
\caption{Exergy destruction and efficiency of air preheat subsystem of novel system} 
\label{fig:novel_APH_exergy}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/LPE_exergy_LMTD.png}
\caption{Exergy efficiency and LMTD of LPEs} 
\label{fig:LPE_exergy_LMDT}
\end{figure}

\subsubsection{Thermodynamic comparison in off-design conditions}
\label{ssub:0ffdesing_compare}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/partload_efficiency.png}
\caption{Exergy efficiency comparison in off-design conditions} 
\label{fig:partload_efficiency}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{fig/partload_subsys_exergyrate.png}
\caption{Exergy destruction rate difference of subsystems in off-design conditions} 
\label{fig:partload_subsys_exergyrate}
\end{figure}

% subsubsection subsubsection_name (end)

\section{Conclusion}
This study presents an optimization design of cascaded utilization of energy for a 1000 MW double reheat ultra-supercritical unit.
 Thermodynamic analysis is conducted to reveal the comprehensive effects of the optimization measures. 
 The optimization system is found to be effective in overcoming the imperfections, and may provide an effective method for the optimization of a double reheat system in USC unit.
  The following conclusions are drawn from this study:

 \begin{enumerate}[(1)]
\item The thermodynamic analysis indicates that the cascaded utilization system decreases the temperature difference of in air heating and flue gas cooling process which achieves the cascaded utilization of energy, and the superheat degree of the 3rd and 5th is reduced greatly. 
Besides, more exhaust heat of the flue gas is recovered since the LPE cools the flue gas to lower temperature. 
\item The layout in the cascaded utilization system changes the mass flow rates of extractions, which causes increment of output power of the generator and increment of the cold source loss.
\item The optimization system improves the temperature of secondary air, which improves the fire condition in the combustion chamber.
 The temperature of secondary air under full load in the optimization model is 365 ℃, which is 34 ℃ higher than the design value.
\item For the first extraction, throttling loss is not existed while the feedwater of boiler improves little.  
\item The optimization system theoretically brings remarkable energy saving effects. The simulation results show that the optimization system can reduce the SCE consumption by 5.6 g/kWh under full load, and can even bring a reduction of 2.9 g/kWh under 50\% THA load .
\end{enumerate}

\section*{References}
\bibliographystyle{elsarticle-num}
